---
title: "Handling missing data"
output: 
  pdf_document:
    toc: TRUE
---

Run this chunk first!
```{r setup}
library(tidyverse)
source('Data_Munging/FACES_fns.R')
```
 
Multiple ways to load data:

```{r include=FALSE}
# first way, specify data
fpath <- read_csv('../Data/FACES_data_Spring_2019_AllData.csv')
format_FACES(data = fpath)

# second way, specify path
format_FACES(path = '../Data/FACES_data_Spring_2019_AllData.csv') # merged cells?

# third way, just call the fucntion
(faces <- format_FACES())
```

### Merged Cells  
Value in merged cells filled accordingly: 
  - Merged Cell gets "unmerged"
  - Value in original merged cell occupies the left most cell after unmerging

## Identifying missing data  
This chunk identifies the missing data by participant, Time, Group, and Survey.

```{r}
(missing_sum <- faces %>%
  filter(is.na(Response)) %>%
  group_by(`Participant #`, Time, Group, Survey) %>%
  summarise(missing_data = sum(is.na(Response))) %>%
  arrange(missing_data) %>% 
  ungroup())
```

### Splitting the missing data  
  - Rule: If a participant is missing 2 or less responses, then we keep the participant; 
    - else: we remove the participant from the affected surveys.
  - The `distinct` function removes instances where the participant is missing more than 2 responses for both a `pre` and `post` time survey response. One instance in either `Pre` or `Post` is enough to get the record removed. 
    
```{r}
keepers <- missing_sum %>%
  filter(missing_data <= 2)

throwers <- missing_sum %>%
  distinct(`Participant #`, Group, Survey, .keep_all = T) %>% # added to removed Pre and Post
  filter(missing_data > 2)
```

### Removing `throwers` from the overall dataset  
  - Right join filters out records
    - Right join by `Participant #`, `Group`, and `Survey` allows the participant records from `Pre` and `Post` to be matched up. 
  - The resulting data set is a list of records that needs to be removed from the original data set

```{r}
(data_to_remove <- faces %>% 
  right_join(throwers, by = c('Participant #', 'Group', 'Survey'),
             suffix = c('', '_mis')))
```

Records removed below: 

```{r}
(faces_clean <-  setdiff(x = faces, y = select(data_to_remove, -Time_mis, -missing_data)))
```

#### Quick checks 

```{r}
# Check that we only took the rows we intended to
nrow(faces_clean) == nrow(faces) - nrow(data_to_remove)

# Check for missing data
anyNA(faces_clean)
```

We still have missing data. Those are from the responses from the missing data in the keepers dataset.

### Imputing the data:  
  - Right join filters out records, again
    - Right join by `Participant #`, `Group`, `Survey`, and `Time` because we only want to impute for that particular missing value
  - Filter down to missing responses, because all questions for each survey category was matched
  - The resulting data set is a list of records that needs to be imputed

```{r}
(data_to_impute <- faces %>%
  right_join(keepers, by = c('Participant #', 'Group', 'Survey', 'Time'),
             suffix = c('', '_kp')) %>%
  filter(is.na(Response)))
```


```{r}
faces_clean2 <- faces_clean %>%
  group_by(Time, Group, Survey, Question) %>%
  mutate(Response = ifelse(is.na(Response), mean(Response, na.rm = T), Response)) %>%
  ungroup()
```

#### Quick check, again 

```{r}
# To visulize what we changed
data_to_impute %>%
  left_join(faces_clean2, by = c('Participant #', 'Time', 'Group', 'Survey', 'Question'),
            suffix = c('_mis', '_fill'))

# Should be true
nrow(faces_clean2) == nrow(faces_clean)

# Should be false
anyNA(faces_clean2)
```

Data is clean beyond previous chunk!


## Summing Responses  
This section pivots the data back to wide after summing up response by Participant for each Time (Pre and Post), Group (Int and Control), and Survey.  
 
```{r}
(faces_sum <- faces_clean2 %>%
   # First group manipulation
  group_by(`Participant #`, Survey, Time, Group) %>%
  summarise(score = sum(Response),
            n_questions = n()) %>%
  ungroup() %>%
   
   # Second group manipulation
  group_by(Survey, Time, Group) %>%
  summarise(mean_participant_score = mean(score),
            spl_size = length(unique(`Participant #`)),
            question_chk = length(unique(n_questions)) == 1) %>%
  ungroup())
```
 
 First group manipulation 
  - `score` is a sum of their responses
  - `n_questions` is the number of questions per survey.
    - Should be the same across comparisons
    
Second group manipulation 
  - `mean_participant_score` is self explanatory. Should match closely with excel pivot table Shantel put together
  - `question_chk` is a check to ensure that the number of questions answered by each participant for each survey is the same while averaging responses. 
  
## Comparison  via Wilcoxon test...  

Did not do that yet, this chunk needs updating.

```{r}
faces_sum %>% 
  pivot_wider(id_cols = c( 'Survey', 'Group'), 
              names_from = contains(c('Time')),
              values_from = c(mean_participant_score, spl_size))
  
```
  
 
 
 