---
title: "Wilcoxon Signed Rank Test"
author: "Joseph Oliveira"
date: "7/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Libraries
library(tidyverse)
library(purrr)
## Loading data:
faces <- read_csv('../Data/cleaned_FACES_data.csv',
                  col_types = c('ffffdf'))

```

## Loading data in from the `Wilcoxon_Test.Rmd` cleaning procedure

```{r}
faces <- faces %>%
  group_by(Group, `Participant #`, Time, Survey) %>%
  summarise(avg_resp = mean(Response)) %>%
  ungroup()
```

Wilcoxon Test function
  
  1. Cleaned `faces` data is filtered for the Time (`Pre` or `Post`) and Group (`Experimental` or `Control`). Depends one what is being compared
  2. Two data sets are created to create the vectors for comparison
  3. 3 Cases need to be handled
    a. If the vector of response variables in data set A are longer than B
    b. If the vector of response variables in data set B are longer than A
    c. If the vector of response variables in data set A and B are equal length

```{r}
faces_wilcox <- function(time1, group1, time2, group2, survey) {
  # Filter to data we need for comparison
  faces_ <- faces %>%
    filter(Time %in% c(time1, time2) & Group %in% c(group1, group2))
  
  # Create 2 datasets
  comp1 <- faces_ %>%
    filter(Time == time1, Group == group1, Survey == survey)
  
  comp2 <- faces_ %>%
    filter(Time == time2, Group == group2, Survey == survey)
  
  # 3 Cases need to be handled:
  # 1. If the lengths are unequal. Sample longer sample to obtain equal comparison
  if (length(comp1$avg_resp) > length(comp2$avg_resp)) {
    
    comp1_spl_resp <- sample(comp1$avg_resp, replace = T, size = length(comp2$avg_resp))
    
    wilcox.test(comp1_spl_resp, comp2$avg_resp)
    
    # Second case for unequal lengths
    } else if (length(comp1$avg_resp) < length(comp2$avg_resp)) {
    
    comp2_spl_resp <- sample(comp2$avg_resp, replace = T, size = length(comp1$avg_resp))
    
    wilcox.test(comp1$avg_resp, comp2_spl_resp)
    
    # if they are equal, then run comparison.
    } else wilcox.test(comp1$avg_resp, comp2$avg_resp)
  }
```

## Creating the comparison groups for the function above. 

```{r}
distinct_groupings <- faces %>%
  distinct(Group, Time, Survey)

dist_grp_exp_pre <- distinct_groupings %>%
  filter(Group == 'Experimental', Time == 'Pre')

dist_grp_ctrl_pre <- distinct_groupings %>%
  filter(Group == 'Control', Time == 'Pre')

dist_grp_exp_post <- distinct_groupings %>%
  filter(Group == 'Experimental', Time == 'Post')

dist_grp_ctrl_post <- distinct_groupings %>%
  filter(Group == 'Control', Time == 'Post')

first_comp <- inner_join(dist_grp_exp_pre, dist_grp_ctrl_pre, by = c("Survey", "Time"))
secnd_comp <- inner_join(dist_grp_exp_post, dist_grp_ctrl_post, by = c("Survey", "Time"))
third_comp <- inner_join(dist_grp_exp_pre, dist_grp_exp_post, by = c("Survey", "Group"))
forth_comp <- inner_join(dist_grp_ctrl_pre, dist_grp_ctrl_post, by = c("Survey", "Group"))

group_comparison <- bind_rows(first_comp, secnd_comp) %>% mutate_all(as.character)

time_comparison <- bind_rows(third_comp, forth_comp) %>% mutate_all(as.character)
```

# Running Wilcoxon tests

```{r message=FALSE, warning=FALSE}
group_wilcoxon <- group_comparison %>%
  mutate(test = pmap(list(time1 = Time, group1 = Group.x, 
                          time2 = Time, group2 = Group.y, 
                          survey = Survey), 
                     faces_wilcox),
         p.value = unlist(map(test, function(x) `$`(`[`(`[`(x)), 'p.value'))))

time_wilcoxon  <- time_comparison %>%
  mutate(test = pmap(list(time1 = Time.x, group1 = Group, 
                          time2 = Time.y, group2 = Group, 
                          survey = Survey),
                     faces_wilcox),
         p.value = unlist(map(test, function(x) `$`(`[`(`[`(x)), 'p.value'))))
```

```{r}
knitr::kable(select(group_wilcoxon, -test) %>%
               group_by(Survey) %>%
               arrange(Survey, p.value, Time))
```

```{r}
knitr::kable(select(time_wilcoxon, -test) %>%
               group_by(Survey) %>%
               arrange(Survey, p.value, Group))
```

