---
title: "Wilcoxon Results Report"
author: "Joseph Oliveira"
date: "7/5/2020"
output: 
  pdf_document:
    toc: TRUE
---


```{r include=FALSE}
library(tidyverse)
library(purrr)
source('Data_Munging/FACES_fns.R')
```

# Comparisons

Each row represents a comparison. 

```{r include=FALSE}
distinct_groupings <- read_csv('../Data/cleaned_FACES_data.csv', col_types = c('ffffdf')) %>%
  distinct(Group, Time, Survey)

dist_grp_exp_pre <- distinct_groupings %>%
  filter(Group == 'Experimental', Time == 'Pre')

dist_grp_ctrl_pre <- distinct_groupings %>%
  filter(Group == 'Control', Time == 'Pre')

dist_grp_exp_post <- distinct_groupings %>%
  filter(Group == 'Experimental', Time == 'Post')

dist_grp_ctrl_post <- distinct_groupings %>%
  filter(Group == 'Control', Time == 'Post')

first_comp <- inner_join(dist_grp_exp_pre, dist_grp_ctrl_pre, by = c("Survey", "Time"))
secnd_comp <- inner_join(dist_grp_exp_post, dist_grp_ctrl_post, by = c("Survey", "Time"))
third_comp <- inner_join(dist_grp_exp_pre, dist_grp_exp_post, by = c("Survey", "Group"))
forth_comp <- inner_join(dist_grp_ctrl_pre, dist_grp_ctrl_post, by = c("Survey", "Group"))

group_comparison <- bind_rows(first_comp, secnd_comp) %>% mutate_all(as.character) %>%
  select(Group.x, Group.y, Time, Survey)

time_comparison <- bind_rows(third_comp, forth_comp) %>% mutate_all(as.character) %>%
  select(Time.x, Time.y, Group, Survey)
```

## Experimental vs. Control Groups 

The total of Pre and the total of Post intervention responses for the Control group is compared to the total of Pre and the total of Post intervention responses for the Experimental group. 

```{r echo=FALSE}
knitr::kable(group_comparison)
```

## Pre vs Post within Experimental and Control Groups

For each the Experimental and the Control group, the total of Pre intervention responses were compared to the total of Post intervention responses. 

```{r echo=FALSE}
knitr::kable(time_comparison)
```

# Results

```{r include=FALSE}
group_wilcoxon <- group_comparison %>%
  # defined the test result
  mutate(test = pmap(list(time1 = Time, group1 = Group.x, 
                          time2 = Time, group2 = Group.y, 
                          survey = Survey), 
                     faces_wilcox, paired = F, alternative = "two.sided"),
         test_statistic = unlist(map(test, function(x) `$`(`[`(`[`(x)), 'statistic'))),
         p.value = unlist(map(test, function(x) `$`(`[`(`[`(x)), 'p.value'))),
         effect_size =  test_statistic / unlist(map(test, function(x) `$`(`[`(`[`(x)), 'obs')))**0.5)

time_wilcoxon  <- time_comparison %>%
  mutate(test = pmap(list(time1 = Time.x, group1 = Group, 
                          time2 = Time.y, group2 = Group, 
                          survey = Survey),
                     faces_wilcox, paired = T, alternative = "less"),
         test_statistic = unlist(map(test, function(x) `$`(`[`(`[`(x)), 'statistic'))),
         p.value = unlist(map(test, function(x) `$`(`[`(`[`(x)), 'p.value'))),
         effect_size = test_statistic / unlist(map(test, function(x) `$`(`[`(`[`(x)), 'obs')))**0.5)
```

## Experimental vs. Control Groups Results

  - $H_0$: There is no difference between the distribution of {*Pre*, *Post*} *Experimental* group survey responses and the distribution {*Pre*, *Post*} *Control* group survey responses.
  - $H_A$: The distribution of the {*Pre*, *Post*} *Experimental* group survey responses $\neq$ the distirbution of the {*Pre*, *Post*} *Control* group survey responses.

```{r echo=FALSE}
knitr::kable(select(group_wilcoxon, Time, Survey, 
                    Group.x, Group.y, 
                    `Test Statistic` = test_statistic, `p` = p.value, `ES` = effect_size) %>%
               group_by(Survey) %>%
               arrange(Survey, p, Time))
```

## Pre vs. Post Results

  - $H_0$: There is no difference between the distribution of {*Experimental*, *Control*} *Pre* survey responses and the distribution of {*Experimental*, *Control*} *Post* survey responses.
  - $H_A$: The mean of the distribution of the {*Pre*, *Post*} *Pre* survey responses $<$ the mean of the distirbution of the {*Pre*, *Post*} *Post* survey responses.

```{r echo=FALSE}
knitr::kable(select(time_wilcoxon, Group, Survey, 
                    Time.x, Time.y, 
                    `Test Statistic` = test_statistic, `p` = p.value, `ES` = effect_size) %>%
               group_by(Survey) %>%
               arrange(Survey, p, Group))
```

Test Statistic from Wilcoxon Test  
p  = P-Value  
ES = Effect Size